Import_Map

### 2024-05-29 Code/Import_MapMireillePro.Rmd
New map

data_textTropicFull <- data.frame(label = c('Season:~All~year~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~Full'))
TropicFull<-ggplot() + 
  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkgreen", linetype = "dashed", alpha=1, size = 1) +
  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.2) +
  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +

@@

data_textSpringFull <- data.frame(label = c('Season:~Spring/Fall~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~Full'))
SpringFull<-ggplot() + 
  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.2) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textSpringFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsSpringFull), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
SpringFull

data_textSummerFull <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~16~h~~~~~~~~Oxygen:~Full'))
SummerFull<-ggplot() + 
  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.2) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textSummerFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsSummerFull), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
SummerFull

data_textWinterFull <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~8~h~~~~~~~~Oxygen:~Full'))
WinterFull<-ggplot() + 
  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.2) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsWinterFull), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        #axis.title.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
WinterFull

@@

data_textTropicOMZ <- data.frame(label = c('Season:~All~year~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~OMZ'))
TropicOMZ<-ggplot() + 
  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkgreen", linetype = "dashed", alpha=0.9, size = 1) +
  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +

@@

data_textSpringOMZ <- data.frame(label = c('Season:~Spring/Fall~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~OMZ'))
SpringOMZ<-ggplot() + 
  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textSpringOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsSpringOMZ), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
SpringOMZ

data_textSummerOMZ <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~16~h~~~~~~~~Oxygen:~OMZ'))
SummerOMZ<-ggplot() + 
  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textSummerOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsSummerOMZ), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
SummerOMZ

data_textWinterOMZ <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~8~h~~~~~~~~Oxygen:~OMZ'))
WinterOMZ<-ggplot() + 
  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textWinterOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsWinterOMZ), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        #axis.title.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
WinterOMZ

@@

data_textTropicFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clade~HLI'))
data_textTropicFullRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
TropicFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textTropicFullRainbowSurface, aes(x=500, y=215, label=label), size=4.5, parse=TRUE) +
  geom_text(data=data_textTropicFullRainbowDeep, aes(x=515, y=90, label=label), size=4.5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
TropicFullRainbow

data_textSpringFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clade~HLI'))
data_textSpringFullRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SpringFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSpringFullRainbowSurface, aes(x=500, y=215, label=label), size=4.5, parse=TRUE) +
  geom_text(data=data_textSpringFullRainbowDeep, aes(x=515, y=90, label=label), size=4.5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SpringFullRainbow

>>>>

data_textTropicFull <- data.frame(label = c('Season:~All~year~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~Full'))
TropicFull<-ggplot() + 
  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkgreen", linetype = "dashed", alpha=1, size = 1) +
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +

@@

data_textSpringFull <- data.frame(label = c('Season:~Spring/Fall~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~Full'))
SpringFull<-ggplot() + 
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textSpringFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsSpringFull), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
SpringFull

data_textSummerFull <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~16~h~~~~~~~~Oxygen:~Full'))
SummerFull<-ggplot() + 
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textSummerFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsSummerFull), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
SummerFull

data_textWinterFull <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~8~h~~~~~~~~Oxygen:~Full'))
WinterFull<-ggplot() + 
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsWinterFull), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        #axis.title.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
WinterFull

@@

data_textTropicOMZ <- data.frame(label = c('Season:~All~year~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~OMZ'))
TropicOMZ<-ggplot() + 
  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkgreen", linetype = "dashed", alpha=0.9, size = 1) +
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +

@@

data_textSpringOMZ <- data.frame(label = c('Season:~Spring/Fall~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~OMZ'))
SpringOMZ<-ggplot() + 
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textSpringOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsSpringOMZ), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
SpringOMZ

data_textSummerOMZ <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~16~h~~~~~~~~Oxygen:~OMZ'))
SummerOMZ<-ggplot() + 
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textSummerOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsSummerOMZ), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
SummerOMZ

data_textWinterOMZ <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~8~h~~~~~~~~Oxygen:~OMZ'))
WinterOMZ<-ggplot() + 
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textWinterOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsWinterOMZ), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        #axis.title.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
WinterOMZ

@@

data_textTropicFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clade~HLI'))
data_textTropicFullRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
TropicFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textTropicFullRainbowSurface, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
  geom_text(data=data_textTropicFullRainbowDeep, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
TropicFullRainbow

data_textSpringFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clade~HLI'))
data_textSpringFullRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SpringFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSpringFullRainbowSurface, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
  geom_text(data=data_textSpringFullRainbowDeep, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SpringFullRainbow
